### 2021-03-13 article/paper_eng.tex
style

\documentclass[a4paper,10pt]{article}
\usepackage[T2A]{fontenc}
\usepackage{sectsty}
\usepackage{changepage}
\usepackage{filecontents}
\usepackage{array}
\usepackage{float} 
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage{physics} 
\usepackage{graphicx}
\usepackage{enumerate}
\graphicspath{{../misc/}}
\usepackage{setspace,amsmath}
\usepackage{bigstrut}
\usepackage{tabularx}
\usepackage[left=15mm, right=15mm, top=15mm, bottom=15mm]{geometry} 
\usepackage[nottoc]{tocbibind}
\usepackage[
style=chem-biochem,
sorting=nyt,
backend=biber,
defernumbers=false,
citestyle=authoryear
]{biblatex}

@@

When using a \textbf{linear classifier}, the sums of spikes of individual  $ Y $ layer neurons are fed as features to te classifier, which is trained to predict the true image labels. As in other methods of interpreting the network activity, classifier training is performed on a separate calibration sample.

>>>>

\documentclass[a4paper,10pt]{article}
\usepackage[T2A]{fontenc}
\usepackage{sectsty}
\usepackage{changepage}
\usepackage{filecontents}
\usepackage{array}
\usepackage{float} 
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage{physics} 
\usepackage{graphicx}
\usepackage{enumerate}
\graphicspath{{../misc/}}
\usepackage{setspace,amsmath}
\usepackage{bigstrut}
\usepackage{tabularx}
\usepackage[left=15mm, right=15mm, top=15mm, bottom=15mm]{geometry} 
\usepackage[nottoc]{tocbibind}
\usepackage[
citestyle=authoryear,
sorting=nyt,
backend=biber,
defernumbers=false,
citestyle=authoryear,
bibstyle=numeric,
firstinits=true
]{biblatex}

\renewbibmacro{in:}{%
  \ifentrytype{article}{}{%
  \printtext{\bibstring{in}\intitlepunct}}}

@@

When using a \textbf{linear classifier}, the sums of spikes of individual  $Y$ layer neurons are fed as features to te classifier, which is trained to predict the true image labels. As in other methods of interpreting the network activity, classifier training is performed on a separate calibration sample.
